Dominance Regions for Rank Two Cluster Algebras

### 2022-04-07 dominance_regions.tex
Monotonicity

  \begin{lemma}
    \label{le:transformed inequalities}
    Let $A$ be an invertible $2\times 2$ matrix.
    Under the left action of $A$, say $A\bfx=\bfy$ for $\bfx,\bfy\in\RR^2$, the region inside $\RR^2$ defined by the inequality $\bfr\bullet(\bfx-\lambda)\le t$ with $\lambda,\bfr\in\RR^2$ and $t\in\RR$ is transformed into the region defined by the inequality \[(A^{-T}\bfr)\bullet(\bfy-A\lambda)\le t.\]
  \end{lemma}
  \begin{proof}
    This is immediate from the equalities
    \[\bfr\bullet(\bfx-\lambda)=\bfr^T(\bfx-\lambda)=\bfr^TA^{-1}A(\bfx-\lambda)=(A^{-T}\bfr)^T(A\bfx-A\lambda)=(A^{-T}\bfr)\bullet(\bfy-A\lambda).\]
  \end{proof}

>>>>

  \begin{lemma}
    \label{le:transformed inequalities}
    Let $A$ be an invertible $2\times 2$ matrix.
    Under the left action of $A$, say $A\bfx=\bfy$ for $\bfx,\bfy\in\RR^2$, the region inside $\RR^2$ defined by the inequality $\bfr\bullet\bfx \le t$ with $\bfr\in\RR^2$ and $t\in\RR$ is transformed into the region defined by the inequality \[(A^{-T}\bfr)\bullet\bfy\le t.\]
  \end{lemma}
  \begin{proof}
    This is immediate from the equalities
    \[\bfr\bullet\bfx=\bfr^T\bfx=\bfr^TA^{-1}A\bfx=(A^{-T}\bfr)^TA\bfx=(A^{-T}\bfr)\bullet\bfy.\]
  \end{proof}
